---
title: "Phd Time series Analysis"
author: "Sai teja Gollapinni"
date: "November 18, 2017"
output: html_document
---

###clear the environment  
```{r}
rm(list=ls(all=T))
```
###Loading the data
```{r}
setwd("C:/Users/saite/Documents/PHD 181117")
getwd()
```

##Required Libraries
```{r }
library(forecast)
library(imputeTS)

```
###Read the data and other Preprocessing
```{r}
Traindata_sales= read.csv(file = "Train.csv",sep=",", header = T)
sum(is.na(Traindata_sales))
colSums(is.na(Traindata_sales))
names(Traindata_sales)
colnames(Traindata_sales)[4] = 'SalesInThousandDollars'
dim(Traindata_sales)
head(Traindata_sales,10)
str(Traindata_sales)
summary(Traindata_sales)
```

##Split the data into three categories
```{r}
sales_Male =Traindata_sales[which(Traindata_sales$ProductCategory == "MenClothing"),]
sales_Female =Traindata_sales[which(Traindata_sales$ProductCategory == "WomenClothing"),]
sales_Others =Traindata_sales[which(Traindata_sales$ProductCategory == "OtherClothing"),]
sum(is.na(sales_Male))
sum(is.na(sales_Female))
sum(is.na(sales_Others))
```
##NA and Imputations
```{r}
sales_Male_Intp=na.interpolation(sales_Male)
sales_Male_locf=na.locf(sales_Male)
sales_Female_Intp=na.interpolation(sales_Female)
sales_Female_locf=na.locf(sales_Female)
sales_Others_Intp=na.interpolation(sales_Others)
sales_Others_locf=na.locf(sales_Others)
```
##Time series models
```{r}
Salesmale = ts(sales_Male_locf$SalesInThousandDollars, frequency = 12, start = c(2009,1))
salesfemale=ts(sales_Female_locf$SalesInThousandDollars,frequency = 12,start = c(2009,1))
salesothers=ts(sales_Others_locf$SalesInThousandDollars,frequency = 12,start = c(2009,1))
```
#plot the time series male
```{r}
par(mfrow=c(1,3))
pacf(Salesmale)
par(mfrow=c(1,3))
Acf(Salesmale)
pacf(salesfemale)
Acf(salesfemale)
pacf(salesothers)
Acf(salesothers)

plot.ts(Salesmale)
plot.ts(salesfemale)
plot.ts(salesothers)

```
###Train test split
```{r}
library(forecast)
Sales_trainm = subset(sales_Male_locf, Year!="2015")
Sales_testm = subset(sales_Male_locf, Year =="2015")
Maletrain_ts=ts(Sales_trainm$SalesInThousandDollars,frequency = 12,start = c(2009,1))
Maletest_ts=ts(Sales_testm$SalesInThousandDollars,frequency = 12,start = c(2015,1))
SalesHW <-  HoltWinters(Maletrain_ts)
summary(SalesHW)
SalesHW$fitted
plot(SalesHW)
MAPE_train_HW = mean(abs(Maletrain_ts-SalesHW$fitted[,"xhat"])/abs(Maletrain_ts))*100
```
##Forecast##
```{r}
Salesforecast_HW = forecast:::forecast.HoltWinters(SalesHW, h=12)
MAPE_test_HW = mean(abs(Maletest_ts - Salesforecast_HW$mean)/abs(Maletest_ts))*100
forecast:::plot.forecast(Salesforecast_HW, shadecols="oldstyle")
```
## Auto Arima
```{r}
SalesMale_autoArima = auto.arima(Maletrain_ts, ic='aic')
Salesforecast_autoArima = forecast:::forecast.Arima(SalesMale_autoArima,h=12)
forecast:::plot.forecast(Salesforecast_autoArima)
MAPE_train_AutoArima =mean(abs(Maletrain_ts -SalesMale_autoArima$fitted)/abs(Maletrain_ts))*100
MAPE_test_AutoArima <- mean(abs(Maletest_ts-Salesforecast_autoArima$mean)/abs(Maletest_ts))*100
```
##HoltWinters
```{r}
ProdCat_Male = ts(sales_Male_locf$SalesInThousandDollars, frequency = 12,start=c(2009,1))
Prodcat_HW =  HoltWinters(ProdCat_Male)
Prodcat_HW= forecast:::forecast.HoltWinters(Prodcat_HW, h=12)
forecast:::plot.forecast(Prodcat_HW, shadecols="oldstyle")
```
write.csv(Prodcat_HW, file = "SubmissionHw1.csv", row.names = F)
```
##Auto Arima
```{r}
Prodcat_Autoarima =  auto.arima(ProdCat_Male)
Prodcat_Autoarima = forecast:::forecast.Arima(Prodcat_Autoarima,h=12)
write.csv(Prodcat_Autoarima, file = "submDataAA1.csv", row.names = F)
```
######Female####################################################################
#####Train test split
```{r}
library(forecast)
Sales_trainf = subset(sales_Female_locf, Year!="2015")
Sales_testf = subset(sales_Female_locf, Year =="2015")
Femaletrain_ts=ts(Sales_trainf$SalesInThousandDollars,frequency = 12,start = c(2009,1))
Femaletest_ts=ts(Sales_testf$SalesInThousandDollars,frequency = 12,start = c(2015,1))
femaleSalesHW <-  HoltWinters(Femaletrain_ts)
#femaleSalesHW$fitted
MAPE_trainf_HW = mean(abs(Femaletrain_ts-SalesHW$fitted[,"xhat"])/abs(Femaletrain_ts))*100
########Forecast##
FemaleSalesforecast_HW = forecast:::forecast.HoltWinters(femaleSalesHW, h=12)
MAPE_testf_HW = mean(abs(Femaletest_ts - FemaleSalesforecast_HW$mean)/abs(Femaletest_ts))*100
forecast:::plot.forecast(FemaleSalesforecast_HW, shadecols="oldstyle")
```
## Auto Arima
```{r}
SalesFemale_autoArima = auto.arima(Femaletrain_ts, ic='aic')
Salesforecast_autoArimaf <- forecast:::forecast.Arima(SalesFemale_autoArima,h=12)
forecast:::plot.forecast(Salesforecast_autoArimaf)
MAPE_trainf_HW = mean(abs(Femaletrain_ts - femaleSalesHW$fitted[,"xhat"])/abs(Femaletrain_ts))*100
MAPE_trainf_AutoArima <- mean(abs(Femaletrain_ts - SalesFemale_autoArima$fitted)/abs(Femaletrain_ts))*100
MAPE_testf_AutoArima <- mean(abs(Femaletest_ts - Salesforecast_autoArimaf$mean)/abs(Femaletest_ts))*100
```
##HoltWinters
```{r}
ProdCat_Female = ts(sales_Female_locf$SalesInThousandDollars, frequency = 12,start=c(2009,1))
Prodcat_HW_f <-  HoltWinters(ProdCat_Female)
Prodcat_HW_f <- forecast:::forecast.HoltWinters(Prodcat_HW_f, h=12)
write.csv(Prodcat_HW_f, file = "Submission2.csv", row.names = F)
##AutoArima
Prodcat_Autoarimaf <-  auto.arima(ProdCat_Female)
Prodcat_Autoarimaf <- forecast:::forecast.Arima(Prodcat_Autoarimaf,h=12)
write.csv(Prodcat_Autoarimaf, file = "submDataAA2.csv", row.names = F)
```
######Others############################################################
###Train test split
```{r}
library(forecast)
Sales_traino = subset(sales_Others_locf, Year!="2015")
Sales_testo = subset(sales_Others_locf, Year =="2015")
Othertrain_ts=ts(Sales_traino$SalesInThousandDollars,frequency = 12,start = c(2009,1))
Othertest_ts=ts(Sales_testo$SalesInThousandDollars,frequency = 12,start = c(2015,1))
OthersSalesHW = HoltWinters(Othertrain_ts)
#summary(SalesHW)
#femaleSalesHW$fitted
MAPE_trainO_HW = mean(abs(Othertrain_ts-OthersSalesHW$fitted[,"xhat"])/abs(Othertrain_ts))*100
########Forecast
OtherSalesforecast_HW = forecast:::forecast.HoltWinters(OthersSalesHW, h=12)
MAPE_testO_HW = mean(abs(Othertest_ts - OtherSalesforecast_HW$mean)/abs(Othertest_ts))*100
forecast:::plot.forecast(OtherSalesforecast_HW, shadecols="oldstyle")
```
## Auto Arima
```{r}
SalesOther_autoArima = auto.arima(Othertrain_ts, ic='aic')
Salesforecast_autoArimaO <- forecast:::forecast.Arima(SalesOther_autoArima,h=12)
forecast:::plot.forecast(Salesforecast_autoArimaO)
MAPE_trainO_HW = mean(abs(Othertrain_ts - OthersSalesHW$fitted[,"xhat"])/abs(Othertrain_ts))*100

MAPE_trainO_AutoArima = mean(abs(Othertrain_ts - SalesOther_autoArima$fitted)/abs(Othertrain_ts))*100

MAPE_testO_AutoArima = mean(abs(Othertest_ts -Salesforecast_autoArimaO$mean)/abs(Othertest_ts))*100
```
##HoltWinters
```{r}
ProdCat_other = ts(sales_Others_locf$SalesInThousandDollars, frequency = 12,start=c(2009,1))
Prodcat_HW_O =  HoltWinters(ProdCat_other)
Prodcat_HW_O <- forecast:::forecast.HoltWinters(Prodcat_HW_O, h=12)
write.csv(Prodcat_HW_O, file = "Submission3.csv", row.names = F)
```
##Auto Arima
```{r}
Prodcat_AutoarimaO <-  auto.arima(ProdCat_other)
Prodcat_AutoarimaO <- forecast:::forecast.Arima(Prodcat_AutoarimaO,h=12)
write.csv(Prodcat_AutoarimaO, file = "submDataAA3.csv", row.names = F)
```{r}