---
title: "Multiple Linear Regression on Customer Data"
author : "Insofe Lab Session"
date: "July 02 , 2017"
output:
  html_document:
    toc_depth: 3
    toc_float: true
  

---
```{r}
# Go through the data and understand the attributes to get the info of the variables.
```

Write a code to clear the environment if needed
```{r}
rm(list = ls(all=T))
```

Write a code to set the working directory.
```{r }
setwd("C:/Users/saite/Desktop/Customer data assignment/MLR assignment")
getwd()
```
Think and load the libraries as and when required in this place only as best practice
```{r}
#for error evaluation matrix
#Impute the missing values using the "centralImputation()" function from the DMwR package
library(DMwR)
#Standardizing the data 
#decostand Using Z score method
library(vegan)
# Correlation Plot
library(corrplot)
# The "preProcess()" function creates a model object required for standardizing unseen data
library(caret)
#stepAIC model
#for "stepAIC()" function
library(MASS)
# Modifying the Model with the VIF
# for "vif()" function 
library(car)
```
Write a code to read the csv file as "data" as per required
```{r eval=TRUE }
customer_data= read.csv("20170702_Batch30_CSE7302c_CustomerData_Assignment.csv", sep = ",", header = T)

```
Write a code to know the names of the attributes
```{r}
names(customer_data)

```
Write a code to find the dimensions of the data
```{r}
dim(customer_data)
```

Write a code to see the head  and tail of the dataset atleast 10rows
```{r }
head(customer_data,10)
tail(customer_data,10)
```
Write a code to see the data types of the attributes 
```{r }
str(customer_data)

```
Write a code to remove the unuseful variables and store the data 
```{r }
customer_data<- customer_data[,-c(1,2)]
colnames(customer_data)
```
Write a code to observe the variables and convert them into the required formats
```{r}
##data_num[,num_Attr] <- data.frame(apply(data_num[,num_Attr],2,function(x) as.numeric(x)))



```
Check the changes again using str() command
```{r }
##str(object = data_num)

```
Write a Code to seperate the target
```{r}
orig_data_without_target = customer_data[,-c(12)]
colnames(orig_data_without_target)

```
Write a code to get the numerical attributes out and store them as data_num
```{r }
cat_Attr <- c("FavoriteGame","FavoriteChannelOfTransaction")
num_Attr <- setdiff(x = names(orig_data_without_target),y = cat_Attr)

data_num <- orig_data_without_target[num_Attr]
str(data_num)

```
Write a code to observe the variables and convert them into the required formats
```{r}
data_num[,num_Attr] <- data.frame(apply(data_num[,num_Attr],2,function(x) as.numeric(x)))



```
Check the changes again using str() command
```{r }
str(object = data_num)

```
Write a code for Normalizing the data_num
```{r}
data_num <- decostand(data_num,"standardize") # Using Z score method
summary(data_num)

```
Write a code to observe the correlation between the  attributes 
```{r}

corrplot(cor(data_num), method = "number")
```
Write a code to plot the corrplot of correlation between the attributes
```{r}
#done already 

```
Write a code to seperate the categorical attributes
```{r}
cat_Attr <- c("FavoriteGame","FavoriteChannelOfTransaction")

data_cat <- orig_data_without_target[cat_Attr]
str(data_cat)

```
Write a code to combine the numerical,categorical data along with the target 
```{r}
str(customer_data)
df_final_customer_data = cbind(data_num,data_cat,customer_data[,12, drop=FALSE])

str (df_final_customer_data)


```
Write a code to set the seed and comment why it is used.
```{r}
set.seed(29)
#seeding is done, so that each time after random data split we get exactly the same dataset for training and testing.

```
Write a code to get the train rows using sample 
```{r}
train_rows <- sample(x = 1:nrow(df_final_customer_data), size = 0.7*nrow(df_final_customer_data))



```
Write a code to get the train and test 
```{r}
train_data <- df_final_customer_data[train_rows, ]

test_data <- df_final_customer_data[-train_rows, ]



```

Write a code to just plot the grahs between attributes and targets
```{r}

par(mfrow = c(2,2))

plot(customer_data$TotalRevenueGenerated, customer_data$NoOfChildren, xlab = "TotalRevenueGenerated", ylab = "NoOfChildren", main = "TotalRevenueGenerated vs NoOfChildren")

plot(customer_data$TotalRevenueGenerated, customer_data$FrquncyOfPurchase, xlab = "TotalRevenueGenerated", ylab = "FrquncyOfPurchase", main = "TotalRevenueGenerated vs FrquncyOfPurchase")

plot(customer_data$TotalRevenueGenerated, customer_data$FrequencyOFPlay, xlab = "TotalRevenueGenerated", ylab = "FrequencyOFPlay", main = "TotalRevenueGenerated vs FrequencyOFPlay")

plot(customer_data$TotalRevenueGenerated, customer_data$NoOfGamesBought, xlab = "TotalRevenueGenerated", ylab = "NoOfGamesBought", main = "TotalRevenueGenerated vs NoOfGamesBought")




```
Write a code to form a linear regression model 
```{r}

model_basic <- lm(TotalRevenueGenerated ~. , data = train_data)

```
Write a code to plot the model
```{r}
par(mfrow = c(2,2))

plot(model_basic)


```
Write a code to check the summary of the model 
```{r}
summary(model_basic)


```
Write a code to predict the value of the target on the linear model 
```{r}
preds_model <- predict(model_basic, test_data[,-c(12)] )


```
Write a code to use stepAIC
```{r}


model_aic <- stepAIC(model_basic, direction = "both")

summary(model_aic)

par(mfrow = c(2,2))
plot(model_aic)

```
Write a code to predict it on stepAIC
```{r}

preds_model_aic <- predict(model_aic, test_data[,-c(12)])



```
Write a code to check the multicollinearity in the lm model 
```{r}

vif(model_basic)



```
Write a code to check the plots of the models
```{r}

plot(model_aic)

```

Write a code to check the multicollinearity problem
```{r}

cor(customer_data$FrquncyOfPurchase , customer_data$NoOfGamesBought)

model3 <- lm(formula = TotalRevenueGenerated ~ MinAgeOfChild + MaxAgeOfChild + Tenure + FrequencyOFPlay + NoOfGamesPlayed + FavoriteGame + NoOfChildren + NoOfUnitsPurchased + FavoriteChannelOfTransaction, data = train_data)

summary(model3)

vif(model3)#to check multi collinearity 
preds_model3 <- predict(model3, test_data[,-c(12)])#predict the model on stepAIC
```
Write a code to evaluate the error in the prediction of AIC

```{r}

regr.eval(test_data$TotalRevenueGenerated, preds_model_aic)

```
Write a code to evaluate the error on the prediction of Linear Regression
```{r}
regr.eval(test_data$TotalRevenueGenerated, preds_model_aic)



```

Write a code to evaluate the error on the prediction of model
```{r}
regr.eval(test_data$TotalRevenueGenerated,preds_model3)


