---
title: "Earth quake seismic data Mith"
author: "Sai teja Gollapinni"
date: "August 12, 2017"
output: html_document
---
#clear the variables  
```{r}
rm(list=ls(all=T))
```


#reading the data
```{r }
setwd("C:\\Users\\saite\\Desktop\\Mith12817")
getwd()
library(foreign)
SeismicinTrain<-read.arff("train.arff")
SeismicinTest<- read.arff("test.arff")
Validation<-read.arff("validation.arff")
```

## Including Plots

You can also embed plots, for example:

```{r}
library(lattice)
library(ggplot2)
library(caret)
```
#Knowing the attribues
```{r}
str(SeismicinTrain)
str(SeismicinTest)
str(Validation)

#sum(is.na(SeismicinTrain))
#na.omit(SeismicinTrain)
#str(SeismicinTrain)
```
#Finding out the zero variables
```{r}
library(caret)
Unvaryingvarible<-nearZeroVar(SeismicinTrain, saveMetrics= TRUE)
Unvaryingvarible
```
#removing zero var
```{r}
library(dplyr)
SeismicinTrain<-SeismicinTrain %>% select(-c(Attr15,Attr16 ,Attr17 ))
```

#removing Na and imputing 
```{r}
#colMeans(is.na(SeismicinTrain))
#colSums(is.na(SeismicinTrain))
sum(is.na(SeismicinTrain))
library(DMwR)
SeismicinTrain<-centralImputation(data=SeismicinTrain)
#rm(SeismicinTrain_Imputed)
sum(is.na(SeismicinTrain))
```

#removing with high correlation 
```{r}
SeismicinTrain$class<-as.factor(as.character(SeismicinTrain$class))
toCorrelate<-SeismicinTrain %>% select(-c(Attr2,Attr3,Attr4,Attr9 ,class))
```

```{r}
correlationMatrix <- cor(toCorrelate)
print(correlationMatrix)
```

```{r}
correlationMatrix[upper.tri(correlationMatrix)]<-0#this way I only pick one of the mirror-imaged highly correlated pair
diag(correlationMatrix)<-0#and I don't remove the highly-correlated-with-itself group
print(correlationMatrix)
```
#Apply 85 percent correlation after removing high correlated groups 
```{r}
apply(correlationMatrix,2, function(x) any(abs(x)>=0.85))
```

```{r}
cor(toCorrelate$Attr18, toCorrelate)
```

```{r}
SeismicinTrain<-SeismicinTrain %>% select(-Attr18)
```

```{r}
sd(SeismicinTrain$Attr14)
sd(SeismicinTrain$Attr13)
sd(SeismicinTrain$Attr12)
sd(SeismicinTrain$Attr11)

#dropping variable with least deviation.
SeismicinTrain<-SeismicinTrain %>% select(-Attr14)
```
#build the Logistic reg model 
```{r}
set.seed(42)

Seismic_logisticmod<-train(class ~ ., data=SeismicinTrain, method="glm")
#confusionMatrix(predict(Seismic_logisticmod,SeismicinTrain), reference=SeismicinTrain$class, positive="1")
#summary(Seismic_logisticmod)


```
#preprocessing for validation 
```{r}
Validation$class=as.factor(as.character(Validation$class))

library(caret)
Unvaryingvarible1<-nearZeroVar(Validation, saveMetrics= TRUE)
Unvaryingvarible1
```

```{r}
library(dplyr)
Validation<-Validation %>% select(-c(Attr15,Attr16 ,Attr17 ))
```


```{r}
#colMeans(is.na(SeismicinTrain))
#colSums(is.na(SeismicinTrain))
sum(is.na(Validation))
```


```{r}
Validation$class<-as.factor(as.character(Validation$class))
toCorrelate1<-Validation %>% select(-c(Attr2,Attr3,Attr4,Attr9 ,class))
```

```{r}
correlationMatrix1<- cor(toCorrelate1)
print(correlationMatrix1)
```

```{r}
correlationMatrix[upper.tri(correlationMatrix)]<-0#this way I only pick one of the mirror-imaged highly correlated pair
diag(correlationMatrix)<-0#and I don't remove the highly-correlated-with-itself group
print(correlationMatrix)
```
#Apply 85 percent correlation after removing high correlated groups 
```{r}
apply(correlationMatrix,2, function(x) any(abs(x)>=0.85))
```

```{r}
cor(toCorrelate1$Attr18, toCorrelate1)
```

```{r}
Validation<-Validation %>% select(-Attr18)
```
#confusion matrix and prediction on test data and submit file generation.
```{r}
sd(Validation$Attr14)
sd(Validation$Attr13)
sd(Validation$Attr12)
sd(Validation$Attr11)

#dropping variable with least deviation.
Validation<-Validation %>% select(-Attr14)
#confusionMatrix(predict(Seismic_logisticmod,Validation), reference=Validation$class, positive="1")
pred <-  predict(Seismic_logisticmod,Validation)
library(ROCR)
prob_test<-predict(Seismic_logisticmod,newdata =  SeismicinTest,type="prob")
pred_test= ifelse(prob_test>0.05,1,0)
confusionMatrix(Validation$class,pred)
submit <-  as.data.frame(cbind(as.numeric(SeismicinTest[,1]),pred_test))
#rm(submit)
#df$class = ifelse(df$class > 2,0,1)
colnames(submit)<- c("Attr1","class")
df <- submit

write.csv(df, file = "MyDataGLm.csv", row.names = F)

```


