---
title: "MCS GA assignment"
author: "Sai teja Gollapinni"
date: "Sept 2, 2017"
output: html_document
---
# Monte Carlo Assignment
#problem statement
There is a 90% and 10% chance of winning full and part projects
respectively. Full project will have 20-24 modules and part project will 10-12 modules.
There are about 50-100 tasks per modules and each task will take 5-10 days. The
resources vary between 3 to 7. What is the most likely time to complete the project?

#clear the environment
```{r}
rm(list=ls(all=T))
```

#Function to give output of time needed for no of simulations(input)
```{r}
noofDaysneeded=function(numSims){
  time=0
for(i in 1:numSims){
  FullorPart= runif(1,0,1)
## #90 % and 10 % for full and part respectively
if(FullorPart<=0.1)   {  #part project probbality and it takes 10-12 modules 
TotalModules=sample(10:12, 1)
}
else{
#probability greater than 10% since 90 is for full time
TotalModules=sample(20:24, 1)
}
##Random generation values(vectors) for tasks and noof people per module
NooftasksperModule= sample(50:100, TotalModules, replace=T)
TotalTasks= sum(NooftasksperModule)
##calculating time taken for all the tasks as it is given that it takes atleast 5-10 days per each task
TimetoDoTasks= sum(sample(5:10, TotalTasks, replace = T))
#randomly generate no of resources as its given that it ranges from 3-7
NoofResources=sample(3:7, 1,replace = T)

#Time required for those tasks to complete with respect to the above simulation: Total time /resource
Days= TimetoDoTasks/NoofResources
}
cat("Days required is : ", Days, "for", numSims, "simulations", "\n")
}
```
##  Final Simulation steps
```{r}
#no of times simulation performed 
numSims =c(10,100,1000, 10000,100000,1000000)
for(i in numSims)
{  
  Days= noofDaysneeded(i)
  }

```