---
title: "Svd text mining assignment"
author: "Sai teja Gollapinni"
date: "August 11, 2017"
output: html_document
---
# Dataset:Newsgroups - sci.med& sci.space
# 1: Creating a corpus
# 2: Preprocessing operations
# 3: Creating Document-Term matrix
# 4: Apply SVD on Document-Term matrix
# 4: Converting the "U" Matrix into Data Frame
# 5: Including class information
# 6: Classification of documents
#    1: Using a kNN classifier
#    2: Using a Decision Tree classifier
#    3: Using a Neural Net
#    4: Using a Naive Bayes Classifier
# Set Working Directory
```{r}
rm(list=ls(all=T))
path <- getwd()
setwd(choose.dir())
getwd()
```

# load required library for handling text
```{r}
library(tm)
```

# Create a corpus - a collection of text documents
```{r}
getSources()
getReaders()
train.med = Corpus(DirSource("sci.med"),
                    readerControl = list(language='en_US'))
```
#writeCorpus(train.med,"temp")
```{r}
train.med[[1]]
as.character(train.med[[1]])
length(train.med)
inspect(train.med[1])
meta(train.med[[1]])

train.space = Corpus(DirSource("sci.space"),
                     readerControl = list(language='en_US'))
test.med= Corpus(DirSource("sci.med"),
                   readerControl = list(language='en_US'))
test.space = Corpus(DirSource("sci.space"),
                    readerControl = list(language='en_US'))
```
# Create a common corpus
```{r}
Corp_tot = c(train.med,train.space,test.med,test.space)
Corp_tot = Corpus(VectorSource(unlist(Corp_tot)))
rm(train.med,train.space,test.med,test.space)
```
# Necessary preprocessing
```{r}
toSpace <- content_transformer(function(x, pattern) gsub(pattern, " ", x))
docs <- tm_map(Corp_tot, toSpace, "/")
docs <- tm_map(Corp_tot, toSpace, "@")
docs <- tm_map(Corp_tot, toSpace, "\\|")

Corp_tot = tm_map(Corp_tot, removePunctuation)

Corp_tot = tm_map(Corp_tot, removeNumbers)

Corp_tot = tm_map(Corp_tot, tolower)

Corp_tot = tm_map(Corp_tot, removeWords, stopwords("english"))
#Corp_tot = tm_map(Corp_tot, removeWords, c(stopwords("english"),"organization","lines","can"))
Corp_tot
Corp_tot = tm_map(Corp_tot, stemDocument, language="english")

Corp_tot = tm_map(Corp_tot, stripWhitespace)

as.character(Corp_tot[[1]])
```
#Constructs or coerces to a document-term matrix
```{r}
dt_matrix <-DocumentTermMatrix(Corp_tot, 
                               control=list(weighting=weightTfIdf, 
                                            minWordLength=2, 
                                            minDocFreq=5)) 
dt_matrix
inspect(dt_matrix[1:2,1:5])
```
# Remove sparse terms from a document-term matrix
```{r}
dt_matrix <- removeSparseTerms(dt_matrix, 0.90)
```
#Display detailed information on a document-term matrix
```{r}
inspect(dt_matrix[1:2,1:5])

dim(dt_matrix)
```
# Applying SVD on Document-Term Matrix
#princomp uses SVD internally
#prcomp uses aegan 

```{r}
svd = svd(as.matrix(dt_matrix))
matrix = svd$u
```
# Convert to dataframe
```{r}
data = as.data.frame(matrix)
data <- data[apply(data, 1, function(x) !all(x==0)),]
```
# Attach Class label
```{r}
target = as.factor(c(rep('med',1000), rep('spe',1000), rep('spe',1000), rep('med',1000)))
data <- cbind(data,target)


train = data[1:(1000+1000),]
test = data[-c(1:(1000+1000)),]

rm(list = setdiff(ls(),c("train","test","data")))
```
#### Classification Task
# Using Decision Tree

```{r}
library(rpart)
rpart_model = rpart(target~.,train)
table(test$target,predict(rpart_model,test,type = "class"))
```
# Using Naive Bayes
```{r}
library(e1071)
nb_model = naiveBayes(x = train,y = train$target)
table(test$target,predict(nb_model,test[,-146],type = "class"))
```