---
title: "Cluster Analysis for Crime Data"
author: "Clustering INSOFE Lab Assignment"
date: "16 July 2017"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
---

**NOTE** Before starting this assignment please remember to clear your environment, you can do that by running the following code chunk

```{r}


```

# Agenda

* Get the data

* Data pre-processing

* Explore the data

* Hierarchical Clustering

* Kmeans Clustering

* Visualising Clusters and Evaluation


# Problem Description

* In the following Unsupervised Learning activity, you will perform cluster analysis on a dataset that has arrests per 100,000 residents for assault, murder, and rape in each of the 50 US states

* The variable names in the dataset are self explanatory

* So, you will cluster US states based on the crime rates, which can then be passed on to public policy experts to gain insight from it


# Reading & Understanding the Data

* Read in the dataset

```{r}

# Use the setwd() function to get to the directory where the data is present
rm(list=ls(all=T))
setwd("C:/Users/saite/Desktop/Cluster analysis Assignment/cluster-analysis-saitej92-master")
getwd()
crimedata= read.csv("crime_data.csv", header= T, sep = ",")
```

* Use the str() and summary() functions to get a feel for the dataset.

```{r}
str(crimedata)
summary(crimedata)

```

* Take a look at the data using the "head()" and "tail()" functions

```{r}
head(crimedata)
tail(crimedata)

```

# Data pre-processing

* Check for the number of missing values in the dataset

```{r}

sum(is.na(crimedata))


```


* Convert the State names into row names and remove that variable from the dataset

```{r}

rownames(crimedata)=crimedata$State
crimedata$State = NULL


```

* Standardize and scale the data

```{r}
crimedata <- scale(crimedata, center = T, scale = T)


```

# Data exploration

* Visualise the distances between the individual observations using the fviz_dist()

```{r, fig.width=12, fig.height=8}


library(factoextra)

distance <- get_dist(crimedata)

fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))

```

# Hierarchical Clustering

* Cluster the data using the Ward algorithm

```{r}

dist <- dist(crimedata, method = "euclidean")

hc_fit <- hclust(dist, method = "ward.D2")




```

* Plot the dendogram for hierarchical clustering

```{r, fig.height=5, fig.width=10}

plot(hc_fit)

```

* Cut the tree to 4 clusters

```{r}


points_hc <- cutree(hc_fit, k = 4)

crimedata_clusts_hc <- cbind(points_hc, crimedata)

colnames(crimedata_clusts_hc)[1] <- "cluster_hc"
head(crimedata_clusts_hc)

```

* Plot a new dendogram, with each of the clusters being surrounded by a border, using the rect.hclust() function

```{r, fig.height=5, fig.width=10}


plot(hc_fit)

rect.hclust(hc_fit, k = 6, border = "red")


```


# K-Means Clustering

* Build a basic kmeans model with k = 2

```{r}

set.seed(123)
km_basic <- kmeans(crimedata, centers = 2)

str(km_basic)

fviz_cluster(km_basic,crimedata)


```

* Build a scree plot and choose a "k"

```{r}


# Initialize wss to 0

wss <- 0

# From 1 upto upto 10 cluster centers, fit the kmeans model

for (i in 1:10) {
  
  cfit = kmeans(crimedata, centers = i)
  
  # Store the sum of within sum of square
  
  wss[i] <- sum(cfit$withinss)
  
}
plot(1:10, wss, type = "b",xlab = "no of clusters",ylab = "within sum of squares")


set.seed(123)

fviz_nbclust(crimedata, kmeans, method = "wss")





```

* Choose a k and cluster the data

```{r}

# We can choose a k = 4, 5 or 6
#choose k as 4 
km_clust <- kmeans(crimedata, 4, nstart = 10)

# after choosing k as 4, let's store the cluster groupings along with the data in a new data frame

km_points <- km_clust$cluster

# Store the cluster assignments in a new data frame

crimedata_clusts_km <- as.data.frame(cbind(km_clust$cluster, crimedata))

# Look at the head of the data

head(crimedata_clusts_km)
colnames(crimedata_clusts_km)[1] <- "cluster_km"

```

* Visualise the clusters by plotting the data points on the first two principal components

```{r, fig.height=5, fig.width=8}

fviz_cluster(km_clust, crimedata)

```

