---
title: "Association Rules "
author: " "
date: "July 21, 2017"
output: html_document
---
# Problem 3 - Assignment
### Association Rules for "Flight Delay" dataset: Generate the rules and identify the patterns. 

1. Read the data into R

```{r, echo=T}
rm(list=ls(all=T))
setwd("C:/Users/saite/Desktop/A rules assignment/a-rules-assignment-saitej92-master")
flightdata=read.csv(file="FlightDelays.csv", sep=",", header = T)
```


2. Look at the summary of all the variables and convert the following variables as factors 
        + Weather 
        
        + DAY_WEEK 
        + Flight Status
```{r}
summary(flightdata)
cat_attr <- c("Weather","DAY_WEEK","Flight.Status")

flightdata[,cat_attr] <- data.frame(apply(flightdata[,cat_attr],2,function(x) as.factor(as.character(x))))

str(flightdata)

```

3. Bin the numeric variable 'CRS_DEP_TIME' into 4 bins as follows: If time is between 6 AM to 12 noon code as 1 and If the time is between 2 , etc.
```{r}
flightdata$CRS_DEP_TIME = as.numeric(cut(flightdata$CRS_DEP_TIME, 4))
flightdata$CRS_DEP_TIME<- as.factor(as.character(flightdata$CRS_DEP_TIME))
str(flightdata)

```

4. Convert the data frame in a transactions object. Look at the first 6 transactions to understand how 'arules' library requires data to be transformed. Use the below R code to view the transactions data 
```{r}
library(arules)
trans <- as(flightdata, "transactions")

```

5. Apply 'arules' algorithm and play with various support, lift and confidence values.
```{r}
rules<- apriori(trans,parameter= list(sup=0.2,conf=0.6, target="rules"))
```

6. Inspect all the rules.
```{r}
summary(rules)
inspect(rules)
```

7. Filter the rules with specific LHS and RHS conditions 
E.g.; Filter the rules with Flighstatus=0
```{r}
rules.itemfilter1 <- as(subset(rules, subset = rhs %in% 
                        "Flight.Status=0"),
                        "data.frame")

```

8. Filter redundant rules if any
```{r}
rules.sorted <- sort(rules, by="lift")
inspect(rules.sorted)

subset.matrix <- is.subset(rules.sorted, rules.sorted,sparse = FALSE)

subset.matrix[lower.tri(subset.matrix, diag=T)] <- NA
redundant <- colSums(subset.matrix, na.rm=T) >= 1

rules.pruned <- rules.sorted[!redundant]
inspect(rules.pruned)
```

9. Pot and visualize the rules
```{r}
library(arulesViz)
plot(rules.pruned)
```